Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar

### 2022-10-29 FS-CRB-HR-report4.tex
catchup

\begin{document}
\titlehead{US Forest Service Forest Health Protection Grant Progess Report 3}
\title{Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar}
\author{Aubrey Moore, University of Guam}
%\date{Submitted December 30, 2020\\Revised January 28, 2021}
\maketitle
\begin{description}	
	\item[GRANTEE:] Aubrey Moore, University of Guam 
	\item[GRANT YEAR:] 2020
	\item[GRANT NUMBER:] 20-DG-11052021-227
	\item[GRANT PROGRAM:] Forest Health Protection
	\item[GRANT EXPIRATION DATE:] 2022-12-31 (extended)
	\item[DATES COVERED BY THIS REPORT:] 2021-06-01 through 2021-12-31
	\item[GRANT STATUS:] Active
\end{description}

@@

\begin{footnotesize}
\url{https://github.com/aubreymoore/Harmonic-Radar/raw/master/FS-CRB-HR-report3.pdf}
\end{footnotesize}

@@

Progress to date includes:
\begin{itemize}
\item Procurement of harmonic radar equipment and tags
\item Tag fabrication (soldering antennae to diodes) in Matt Siderhurst's lab.
\item Preliminary field testing of equipment on Guam.
\end{itemize}

The most important activity is to conduct field releases and tracking of tagged CRB over a two week intensive fieldwork period. The intensive fieldwork will be performed on Guam in collaboration with Matt Siderhurst's team of students who have experience in tracking insects with harmonic radar. (We are following an approach similar to what we did in the radio-tracking feasibility study). This fieldwork activity has not yet been scheduled because of COVID-19 travel restrictions (See section \ref{impediments} for details.). Otherwise we are prepared to proceed.

@@

Preliminary tests are promising:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (See Technical Report: Using a Cell Phone as a Datalogger for Handheld Harmonic Radar \url{https://github.com/aubreymoore/Harmonic-Radar/blob/master/experiments/techreport/techreport.pdf})	
	\item Flown the RECCO harmonic radar device attached to a drone (Fig. \ref{fig:drone})
	\item \textbf{Based on initial flight tests we determined that the audio data recorder we were using was too heavy for use on the drone. We purchased a much smaller and light audio data recorder. Walk tests with this recorder show that we can locate harmonic radar tags (Fig. \ref{fig:211109003}).}
\end{itemize}

@@

COVID travel restrictions during the current reporting period did not allow Dr. Siderhurst and students to visit Guam to perform the planned field work. Guam is currently experiencing high COVID incidence predominantly caused by the D variant. We are currently targeting spring break 2022 as the time period for field work.

\textbf{As of mid February 2022, Guam is still has extremely high local transmission of COVID due to delayed arrival of the OMICRON variant. However, quarantine for fully vaccinated visitors from the mainland is no longer required. A decision on when Dr. Siderhurst and students experienced with using harmonic radar to track insects will visit Guam to complete planned field work is still pending.}

>>>>

\begin{document}
\titlehead{US Forest Service Forest Health Protection Grant Progess Report 4}
\title{Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar}
\author{Aubrey Moore, University of Guam}
%\date{Submitted December 30, 2020\\Revised January 28, 2021}
\maketitle
\begin{description}	
	\item[GRANTEE:] Aubrey Moore, University of Guam 
	\item[GRANT YEAR:] 2020
	\item[GRANT NUMBER:] 20-DG-11052021-227
	\item[GRANT PROGRAM:] Forest Health Protection
	\item[GRANT EXPIRATION DATE:] 2022-12-31 (extended)
	\item[DATES COVERED BY THIS REPORT:] 2022-01-01 through 2022-06-30
	\item[GRANT STATUS:] Active
\end{description}

@@

\begin{footnotesize}
\url{https://github.com/aubreymoore/Harmonic-Radar/raw/master/FS-CRB-HR-report4.pdf}
\end{footnotesize}

@@

Progress to date includes:
\begin{itemize}
\item Procurement of harmonic radar equipment and tags
\item Tag fabrication (soldering antennae to diodes) in Matt Siderhurst's lab.
\item Preliminary field testing of equipment on Guam.
\item \textbf{Published our research idea as a preprint in the Research Ideas and Outcomes Journal (\href{https://doi.org/10.3897/rio.8.e86422}{Moore and Siderhurst 2022}). This article will be peer reviewed.}
\end{itemize}

The most important activity in our work plan is to conduct field releases and tracking of tagged CRB over a two week intensive fieldwork period. This intensive fieldwork will be performed on Guam in collaboration with Matt Siderhurst's team of students who have experience in tracking insects with harmonic radar. (We are following an approach similar to what we did in the radio-tracking feasibility study \href{https://academic.oup.com/ee/article/46/1/92/2633399?login=false}{Moore et al. 2017}). This fieldwork activity has not yet been scheduled because of COVID-19 travel restrictions (See section \ref{impediments} for details.). Otherwise we are prepared to proceed. \textbf{Our field trial is now planned for July 2022.}

@@

Preliminary tests are promising:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (See Technical Report: Using a Cell Phone as a Datalogger for Handheld Harmonic Radar \url{https://github.com/aubreymoore/Harmonic-Radar/blob/master/experiments/techreport/techreport.pdf})	
	\item Flown the RECCO harmonic radar device attached to a drone (Fig. \ref{fig:drone})
	\item Based on initial flight tests we determined that the audio data recorder we were using was too heavy for use on the drone. We purchased a much smaller and light audio data recorder. Walk tests with this recorder show that we can locate harmonic radar tags by correlating audio recordings with GPS data (Fig. \ref{fig:211109003}).
	\item \textbf{Recent drone flight.}
\end{itemize}

@@

\textbf{COVID travel restrictions during the current reporting period did not allow Dr. Siderhurst and students to visit Guam to perform the planned field work on schedule. Guam still has extremely high local transmission of COVID due to delayed arrival of the OMICRON variant. However, quarantine for fully vaccinated visitors from the mainland is no longer required. Travel arrangements have been made for Dr. Siderhurst and students experienced with using harmonic radar to track insects to visit Guam during July 2022 to complete planned field trial.}
